### 2016-04-25 paper6.tex
Updated to the accepted version.

The mass ratio, period, and eccentricity distributions are well-known for solar type stars \citep{Duquennoy1991, Raghavan2010} and cooler stars \citep{Fischer1992, Delfosse2004}. Interestingly, \citet{Reggiani2011}, and later \citet{Meyer2013}, found that the mass-ratio distribution of field solar-type and M-dwarf stars is invariant to separation. However, the solar-type binary semimajor axis distribution peaks near $45$ AU, and only $\sim 10\%$ of binary systems have separations $a < 100$ AU \citep{Raghavan2010}; the 30 stars used in the analysis by \citet{Reggiani2011} is unsufficient to rule out a separation-variant mass-ratio distribution if it changes outside $a \gtrsim 100$ AU. Field M-dwarf binary systems have typical separations of $\sim 5$ AU \citep{Fischer1992}, and so the 27 stars using in the analysis is again insufficient to look for differences outside of $100$ AU.

All of the orbital distributions are much less certain for more massive stars. The reason for this is two-fold: first, more massive stars tend to be more distant than sunlike or low-mass stars, meaning many of the companions are angularly close to the primaries and difficult to detect with imaging techniques. Second, the primary stars tend to be rapid rotators, which limits radial velocity precision to $\sim 1 \mathrm{km\ s}^{-1}$. Additionally, radial velocity monitoring can only measure a mass ratio if spectral lines from both components are visible; this typically suffers from the same flux ratio difficulty as imaging techniques.

>>>>

The mass ratio, period, and eccentricity distributions are well-known for solar type stars \citep{Duquennoy1991, Raghavan2010} and cooler stars \citep{Fischer1992, Delfosse2004}. Interestingly, \citet{Reggiani2011}, and later \citet{Meyer2013}, found that the mass-ratio distribution of field solar-type and M-dwarf stars is invariant to separation. The field M-dwarf semimajor axis distribution peaks near $\sim 5$ AU \citep{Duchene2013}, with very few companions at separation $\gtrsim 100$ AU; the 27 stars used in the analysis by \citet{Reggiani2011} is unsufficient to compare the mass-ratio distribution inside $\sim 100$ AU with that outside it. However, the solar-type period distribution peaks near $45$ AU \citep{Raghavan2010}, with roughly $40\%$ of binary systems on orbits wider than $100$ AU. The nondetection of a difference in mass-ratio distribution is significant, although with only 30 stars in the field sample it is difficult to completely rule out that such a difference exists.

All of the orbital distributions are much less certain for more massive stars. The reason for this is two-fold: first, more massive stars tend to be more distant than sunlike or low-mass stars, meaning many of the companions are angularly close to the primaries and difficult to detect with imaging techniques. Second, the primary stars tend to be rapid rotators, which limits radial velocity precision to $\sim 1 \mathrm{km\ s}^{-1}$ and causes the spectral lines of double-lined systems to blend. Radial velocity monitoring can only measure a mass ratio if spectral lines from both components are visible and separable; this typically suffers from the same flux ratio difficulty as imaging techniques.
